Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-19 Draft.Rmd
edited knn

# Visualize linear relationship between predictors (lat, lon, state) and value
# Visual of relationship between PM
origin |> ggplot(aes(x=lon, y=value)) + 
  geom_point() + geom_smooth() + 
  labs(title="PM2.5 Concentration (mu g/m^3)", x="Longitude ()", y="PM2.5")

@@

# Check performance of lin. regr. model on the complete training data
res1 %>% 
    extract_fit_engine() %>% 
    summary()

# Check  lin. regr. model performance using cross-validation
folds1 <- vfold_cv(train, v = 10)
folds1
res1 <- fit_resamples(wf1, resamples = folds1)
res1 %>% 
    collect_metrics()
```

>>>>

# Visualize linear relationship between predictors (lat, lon, state) and value
origin |> ggplot(aes(x=lon, y=value)) + 
  geom_point() + geom_smooth() + 
  labs(title="PM2.5 Concentration (mu g/m^3)", x="Longitude (degrees)", y="PM2.5")

@@

# Check performance of linear regression model on the complete training data
res1 %>% 
    extract_fit_engine() %>% 
    summary()

# Check linear regression model performance using cross-validation
folds1 <- vfold_cv(train, v = 10)
folds1
res1 <- fit_resamples(wf1, resamples = folds1)
res1 %>% 
    collect_metrics()
```

```{r kNN}
# Find ideal k clusters

# Scale the training data for k-NN model
train_scales
origin_scaled <- origin %>% 
    mutate(across(-value, scale))

# Create kNN model
model2 <- nearest_neighbor(neighbors = 5) %>% 
    set_engine("kknn") %>% 
    set_mode("regression")

# Create workflow
  wf2 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model2)

# Fit the model on the full training dataset using the `fit()` function
res2 <- fit(wf2, data = train)

# Check performance on the complete training data
res2 %>% 
    extract_fit_engine() %>% 
    summary()

# Check performance using cross-validation
folds <- vfold_cv(train, v = 10)
folds
res2 <- fit_resamples(wf2, resamples = folds) #error Assigned data `orig_rows` must be compatible with existing data.
res2 %>% 
    collect_metrics()
```

```{r Bootstrap}
# Create Bootstrap Model
model3 <- nearest_neighbor(neighbors = 5) %>% 
    set_engine("kknn") %>% 
    set_mode("classification")

# Create workflow
  wf3 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model3)

```{r Random Forests}
# Create Random Forest Model
model4 <- rand_forest(mtry = 5) %>% 
    set_engine("ranger") %>% 
    set_mode("regression")

# Create workflow
  wf4 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model4)
